### 2013-03-28 doc/sosp13/tasks.tex
Fix up the code and API, remove spawn_on.

\begin{figure}[htbp]
  \begin{center}
	\begin{tabular}{l}
    \texttt{\scriptsize spawn( void (*fp)(args) )} \\
      Creates a new stealable task \\
    \texttt{\scriptsize spawn\_on( core, (*fp)(args) )} \\
      Creates a new task that will run on a specific core \\
    \texttt{\scriptsize parallel\_for( (*fp)(args), start, end )} \\
      Executes iterations of a loop as stealable tasks  \\
    \texttt{\scriptsize call\_on( core, (*fp)(args) )} \\ 
      Runs a limited function on a specific core without \\
      consuming \Grappa execution resources 
	\end{tabular}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:expressing-parallelism} \Grappa API: expressing parallelism
      \TODO{update this with latest C++ code from ``api\_examples.cpp''}
      } % \vspace{-4ex}}
    \end{minipage}
    %\vspace{-3ex}
  \end{center}
\end{figure}

\begin{figure}[htbp]
\begin{scriptsize}
\begin{verbatim}

class node_t {
  key_t   key
  int64_t numChildren;
  GlobalAddress<struct node_t *> *children;
};

@@

  parallel_for(0, node->numChildren, &index) {
    search(node->children[index], key);
  }

}
\end{verbatim}
\end{scriptsize}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
	\begin{tabular}{l}
    \texttt{\scriptsize spawn( Functor f )} \\
      Creates a new stealable task \\
    \texttt{\scriptsize parallel\_for( start, end, Functor iteration )} \\
      Executes iterations of a loop as stealable tasks that take the iteration index as an argument  \\
    \texttt{\scriptsize call\_on( core, Functor f )} \\ 
      Runs a limited function on a specific core without \\
      consuming \Grappa execution resources 
	\end{tabular}
    \begin{minipage}{0.95\columnwidth}
      \caption{\label{fig:expressing-parallelism} \Grappa API: expressing parallelism
      \TODO{update this with latest C++ code from ``api\_examples.cpp''}
      } % \vspace{-4ex}}
    \end{minipage}
    %\vspace{-3ex}
  \end{center}
\end{figure}

\begin{figure}[htbp]
\begin{scriptsize}
\begin{verbatim}
class node_t {
  key_t   key
  int64_t numChildren;
  GlobalAddress<node_t *> children;
};

@@

  parallel_for(0, node->numChildren, [=](int index) {
    spawnTask([=]{
      search(node->children[index], key);
    });
  });
}
\end{verbatim}
\end{scriptsize}
\end{figure}
